Hybrid nonlinear system identification using neural networks

### 2020-12-17 systemID_NNs.tex
commit the files.

\subsection{Conversion to discrete time and training}
We note that the network $f_N(\cdot)$ is an addition to the grey-box dynamics in
continuous time in \eqref{eq:hybrid_cont_time}. The Runge-Kutta-4 (RK4) method
is used for the discretization as follows

@@

\subsection{Nonlinear reactor example}
We now demonstrate the application of the above hybrid modeling framework
via a simulation study on a simple chemical process example. We consider a nonlinear reactor with two reactions ($A \rightarrow B $ and  $3B
\rightleftharpoons C$), simulated using the following ordinary differential
equations (ODEs)
\begin{align*}
  \dfrac{dC_A}{dt} &= \dfrac{C_{Af} - C_A}{\tau} - k_1C_A\\
  \dfrac{dC_B}{dt} &= k_1C_A - 3k_2C^3_B + 3k_3C_C- \dfrac{C_B}{\tau}\\
  \dfrac{dC_C}{dt} &= k_2C^3_B - k_3C_C - \dfrac{C_C}{\tau}
\end{align*}

@@

>>>>

\section{Conversion to discrete time and training}
We note that the network $f_N(\cdot)$ is an addition to the grey-box dynamics in
continuous time in \eqref{eq:hybrid_cont_time}. The Runge-Kutta-4 (RK4) method
is used for the discretization as follows

@@

\section{Nonlinear reactor example}
We now demonstrate the application of the above hybrid modeling framework
via a simulation study on a simple chemical process example. We consider a nonlinear reactor with two reactions ($A \rightarrow B $ and  $3B
\rightleftharpoons C$), simulated using the following ordinary differential
equations (ODEs)
\begin{align*}
  \dfrac{dC_A}{dt} &= \dfrac{C_{Af} - C_A}{\tau} - k_1C_A\\
  \dfrac{dC_B}{dt} &= k_1C_A - 3k_2C^3_B + 3k_3C_C- \dfrac{C_B}{\tau}\\
  \dfrac{dC_C}{dt} &= k_2C^3_B - k_3C_C - \dfrac{C_C}{\tau}
\end{align*}

@@

\section{Large, CSTR and flash in series example}
\begin{figure}[!h]
  \centering
  \includegraphics[width=\textwidth, height=0.4\textheight]{cstr_flash.pdf}
  \caption{Schematic of the CSTR and flash plant. The CSTR facilitates two 
  reactions, the first reaction ($A \rightarrow B$) forms the primary product $B$, and the second reaction ($3B \rightarrow C$) 
  consumes the desired product $B$ and forms the undesired product $C$.
  The non-adiabatic flash separates the reactant $A$ and 
  products $B$ and $C$. The major component in the vapor phase 
  is $A$, and it is recycled back after cooling to the CSTR.}
  \label{fig:cstr_flash}
\end{figure}
\newpage
\textbf{Plant -- }
\begin{align*}
  \dfrac{dH_r}{dt} &= \dfrac{F + D -F_r}{A_r}\\
  \dfrac{dC_{Ar}}{dt} &= \dfrac{F(C_{Af} -C_{Ar}) + 
                         D(C_{Ad} -C_{Ar})}{A_rH_r} - r_1 \\
  \dfrac{dC_{Br}}{dt} &= \dfrac{-FC_{Br} + 
                          D(C_{Bd} -C_{Br})}{A_rH_r} + r_1 -3r_2\\
  \dfrac{dC_{Cr}}{dt} &= \dfrac{-FC_{Cr} + 
  D(C_{Cd} -C_{Cr})}{A_rH_r} + r_2\\
  \dfrac{dT_r}{dt} &= \dfrac{F(T_f - T_r) + D(T_d -T_r)}{A_rH_r} + 
                      \dfrac{r_1\Delta H_1 + r_2\Delta H_2}{\rho C_p} + 
                      \dfrac{Q_r}{\rho A_r C_p H_r}\\
  \dfrac{dH_b}{dt} &= \dfrac{F_r - F_b - D}{A_b} \\
  \dfrac{dC_{Ab}}{dt} &= \dfrac{F_r(C_{Ar} -C_{Ab}) + 
                          D(C_{Ab} -C_{Ad})}{A_bH_b} \\
  \dfrac{dC_{Bb}}{dt} &= \dfrac{F_r(C_{Br} -C_{Bb}) + 
                          D(C_{Bb} -C_{Bd})}{A_bH_b} \\
  \dfrac{dC_{Cb}}{dt} &= \dfrac{F_r(C_{Cr} -C_{Cb}) + 
                          D(C_{Cb} -C_{Cd})}{A_bH_b} \\
  \dfrac{dT_b}{dt} &= \dfrac{F_r(T_r - T_b)}{A_bH_b} +
                      \dfrac{Q_b}{\rho A_b C_p H_b}\\
\end{align*}

The sample time for plant measurements is $1$ min, the 
plant states are ($H_r, C_{Ar}, C_{Br}, C_{Cr}, T_r, 
H_b, C_{Ab}, C_{Bb}, C_{Cb}, T_b$), and the measurements are just 
the heights and temperatures of the CSTR and flash. \\

\textbf{Grey-box model -- }
\begin{align*}
  \dfrac{dH_r}{dt} &= \dfrac{F + D -F_r}{A_r}\\
  \dfrac{dC_{Ar}}{dt} &= \dfrac{F(C_{Af} -C_{Ar}) + 
                         D(C_{Ad} -C_{Ar})}{A_rH_r} - r_1 \\
  \dfrac{dC_{Br}}{dt} &= \dfrac{-FC_{Br} + 
                          D(C_{Bd} -C_{Br})}{A_rH_r} + r_1\\
  \dfrac{dT_r}{dt} &= \dfrac{F(T_f - T_r) + D(T_d -T_r)}{A_rH_r} + 
                      \dfrac{r_1\Delta H_1}{\rho C_p} + 
                      \dfrac{Q_r}{\rho A_r C_p H_r}\\
  \dfrac{dH_b}{dt} &= \dfrac{F_r - F_b - D}{A_b} \\
  \dfrac{dC_{Ab}}{dt} &= \dfrac{F_r(C_{Ar} -C_{Ab}) + 
                          D(C_{Ab} -C_{Ad})}{A_bH_b} \\
  \dfrac{dC_{Bb}}{dt} &= \dfrac{F_r(C_{Br} -C_{Bb}) + 
                          D(C_{Bb} -C_{Bd})}{A_bH_b} \\
  \dfrac{dT_b}{dt} &= \dfrac{F_r(T_r - T_b)}{A_bH_b} +
                      \dfrac{Q_b}{\rho A_b C_p H_b}\\
\end{align*}

The grey-box model assumes no knowledge of the second 
reaction ($3B \rightarrow C$), which produces the undesired 
product $C$. Note that since only heights and temperatures are 
measured, all the states in the plant model are 
not observable and only asymptotically detectable.

The economic objective is -- 
\begin{align*}
  \underset{u_s}{\textnormal{min}} \quad 
  \ell(u_s, x_s) \quad := & \quad c_1F + c_2Q_r + 
                                      c_3Q_b - c_4C_{Bb} \\
  x_s &= f(x_s, u_s)\\ 
  y_s &= h(x_s) \\
  \underline{u} \leq &u_s \leq \overline{u}
\end{align*}
